---
title: "markmyassignment"
author: "Mans Magnusson and Oscar Pettersson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{markmyassignment}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The markmyassignment package is a tool to easily get automatic feedback on your lab assignment before turning them in.

### Installing the package

The package is easiest installed in R as follows:

```{r, message=FALSE, eval=FALSE}
install.packages("markmyassignment")
```


### Usage

To use the package markmyassignment, it first needs to be loaded:

```{r, message=FALSE}
library(markmyassignment)
```

Then, use ```set_assignment()``` with the path provided by the teacher. Below is an example assignment that is part of the package. The assignment path depends on the local R installation path.

```{r, message=FALSE}
assignment_path <- 
 paste0(system.file(package = "markmyassignment"), "/extdata/example_assignment01.yml")
set_assignment(assignment_path)
```

Let's look at the tasks included in our assignment. To check which task thats included we use ```show_tasks()```.

```{r}
show_tasks()
```

In this example assignment there are two tasks and also a mandatory requirement.

**Mandatory requirement: **

*Store your name in the variable* ```my_name```*.*

**task1:**

*Create a vector containing the values of $\pi$ and e. The name of the vector should be* ```task1```*.*

**task2:**

*Create a function that takes a numeric vector as argument and returns the sum of the first and last element. Name the function* ```task2```*.*

We start to solve this assignment by solving the first task. It seems to work as intended.

```{r}
task1 <- c(pi, exp(1))
print(task1)
```

We now try to correct our lab using ```markmyassignment```:

```{r}
mark_my_assignment()
```

That did not work too well. This is how it looks when something goes wrong when the ```markmyassignment``` package is used.

The first part of the message contains the names of the tests that are run. The names should only be followed by dots, each dot is symbolising a test that passed (ie a correct part of the actual task). If there are numbers or letters, then there is some kind of problem.

The easiest way go through the error messages is to start with the errors in chronological order. Start with the first error and correct this error and run the ```mark_my_assignment()``` again. Lets look at the first error message:

```
1. Failure: Mandatory tests -------------------------------------------------------------------
Variable my_name is missing
```

We forgot to include our name. For this lab the teacher has decided that this is mandatory. Let's fix this problem.

```{r}
my_name <- "Foo Bar"
mark_my_assignment()
```

Yay! The first problem has been solved! Now we can check the next problem in our assignment.

```
1. Failure: Marking task2 ---------------------------------------------------------------------
task2() does not exist.
```

The second problem is that we tried to mark the second task, but we have not yet tried to solve this assignment. So lets only correct the first task by using the ```tasks``` argument in ```mark_my_assignment()```:

```{r}
mark_my_assignment(tasks = "task1")
```

That worked better - only dots! We have solved the first task. Let's solve the second problem.

```{r}
task2 <- function(vector){
  vector[1] + vector[5]
}
task2(1:5)
```

It seems to work well. Let's see what markmyassignment says.

```{r}
mark_my_assignment(tasks = "task2")
```

Oh! It seems like there is an error in our function. What if we run our function with the same example as markmyassignment does?

```{r}
task2(5:10)
```

Ah, the problem seems to be that we assumed a fixed length vector argument. Lets correct that and check our task again.

```{r}
task2 <- function(vector){
  vector[1] + vector[length(vector)]
}
mark_my_assignment(tasks = "task2")
```

It passed the tests! Now all tasks are done and to be sure, we can now use ```mark_my_assignment()``` to correct the whole lab. But it is important that ```my_name``` and all the objects are in the global environment. To check this, we can use ```ls()```.

```{r}
ls()
mark_my_assignment()
```

Yay! We're done with the computer lab!

If we save our file now, we could even clean the global environment and run the tests on the file. This is also what the teacher will use when correcting the labs (but probably with some extra tests). We need both the file path and the same assignment path that we used to ```set_assignment()```:

```{r}
mark_file <- paste0(system.file(package = "markmyassignment"), "/extdata/example_lab_file.R")
mark_my_file(mark_file = mark_file, assignment_path = assignment_path)
```

We could also check individual tasks in our file, similar to before:

```{r}
mark_my_file(tasks = "task1", mark_file = mark_file, assignment_path = assignment_path)
```

Good luck! If you have any suggestions, comments or ideas feel free to add an issue at  the package [webpage](https://github.com/MansMeg/markmyassignment).

